Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-29 paper/paper.tex
revise frame/context

It is worth noting that the continuation class @Kont@ is defined as a list of
frames, where a frame can be considered a representation of a reduction context
in reduction semantics.
An empty list represents an empty call stack; otherwise, the head frame in the list
represents the innermost context, and the reduction result of this frame will be used
to fill the ``hole'' of its following element in the list.
We represent frames using the @Frame@ class, which stores the information of a single
call-site, i.e., the information that can be used to resume the interrupted computation.
A @Frame@ constitutes a variable name @x@ to be bound later, and a control component
to which the program may resume, as well as its environment.

>>>>

It is worth noting that the continuation class @Kont@ is defined as a list of
frames to represent a reduction context.
An empty list represents an empty context, and corresponds to halt. Otherwise, the head 
frame in the list represents the innermost context, and the reduction result of this 
frame will be used to fill the ``hole'' of its following frame in the list.
We represent frames using the @Frame@ class, which stores the information of a single
call-site, i.e., the information that can be used to resume the interrupted computation.
A @Frame@ constitutes a variable name @x@ to be bound later, and a control component
to which the program may resume, as well as its environment.
